### 2019-05-08 README.Rmd
Install via devtools in README, check_status() to cites_check_status()
Use remotes instead of devtools to install
Make CI badge reflect only master branch

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=shield){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

```{r install_me, eval = FALSE}
source("https://install-github.me/ecohealthalliance/citesdb")
```

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb/tree/master.svg?style=shield){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![](https://badges.ropensci.org/292_status.svg)](https://github.com/ropensci/software-review/issues/292)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

```{r install_me, eval = FALSE}
remotes::install_github("ecohealthalliance/citesdb")
```
